---
title: "Solving probablity distribution problems with R"
author: "Vijayendra Dwari"
date: "02/11/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#A man claims to have extrasensory perception. As a test, a fair coin is flipped 10 times and the man is asked to
#predict the outcome in advance. He gets 7 out of 10 correct. What is the probability that he would have done at least
#this well if he had no ESP?

#Solution : P(X ≥ 7) = P(X = 7) + P(X = 8) + P(X = 9) + P(X = 10)

#=176/1024
```{r}
176/1024
sum(dbinom(7:10,10,0.5))
```


#If you buy a lottery ticket in 50 lotteries, in each of which your chance of winning a prize is 1/100 ,
#what is the (approximate) probability that you will win a prize

```{r}
#a) at least once? P(x>=1) =0.3949939
sum(dbinom(1:50,50,1/100))
# b) exactly once?p(X=1) = 0.3055586
dbinom(1,50,1/100) 
# c) at least twice? = 0.07561
sum(dbinom(2:50,50,1/100))
```


#You arrive at a bus stop at 10 o’clock, knowing that the bus will arrive at some time uniformly 
#distributed between 10 and 10:30.
#a) What is the probability that you will have to wait longer than 10 minutes?

```{r}
punif(10, min = 0, max = 30,lower.tail = F)
```



#b) If at 10:15 the bus has not yet arrived, what is the probability that you will have to what at least an additional
#10 minutes?

```{r}

punif(25, min = 15, max = 30,lower.tail = F)
```



#The annual rainfall (in inches) in a certain region is normally distributed with μ = 40 and σ = 4. 
#What is the probability that, starting with this year, it will take over 10 years before a year occurs having a
#rainfall of over 50 inches? What assumptions are you making?

```{r}
pnorm(50,40,4,lower.tail=T)^10
```

#13. If X is a normal random variable with parameters μ = 10and σ^2 = 36, compute
#a) P{X > 5}


```{r}
pnorm(5, mean = 10, sd = 6, lower.tail=FALSE)
```


#b) P{4<X<16}
```{r}
pnorm(16, mean = 10, sd = 6, lower.tail=TRUE) - pnorm(4, mean = 10, sd = 6, lower.tail=TRUE)
```

#8. Let x be the random variable that represents the speed of cars. x has μ = 90 and σ = 10. 
#We must find the probability that x is higher than 100 or P(x > 100)
```{r}
pnorm(100, mean =90, sd = 10, lower.tail=TRUE)
```

##If the average number of claims handled daily by an insurance company is 5, 

#what proportions of days have less than 3 claims? 
```{r}
sum(dpois(0:2, 5))
```

#What is the probability that there will be 4 claims in exactly 3 of the next 5 days? 
#Assume that the number of claims on different days is independent.
```{r}
dpois(4,5)

choose(5,3) * dpois(4,5)^3 * (1-dpois(4,5))^2
```

#A survey indicates that for each trip to the supermarket, a shopper spends an average μ=45 minutes with a standard deviation of σ=12 minutes. The length of time spent in the store is normally distributed and is represented by the variable x. A shopper enters the store.
#Find the probability that the shopper will be in the store for each interval of time listed below.
#If 200 shoppers enter the store, how many shoppers would you expect to be in the store for each interval of time listed below?

#Find the probability that the shopper will be in the store for each interval of time listed below.
#1) Between 24 and 54 minutes
```{r}

pnorm(54, 45, 12, lower.tail=TRUE) - pnorm(24, 45, 12, lower.tail=TRUE)

200*(pnorm(54, 45, 12, lower.tail=TRUE) - pnorm(24, 45, 12, lower.tail=TRUE))
```

#2) More than 39 minutes

```{r}
pnorm(39, 45, 12, lower.tail=FALSE)

200*pnorm(39, 45, 12, lower.tail=FALSE)
```

#An architect is designing a doorway for a public building to be used by people whose heights are normally 
#distributed, with mean 1 meter 75 centimeter, and standard deviation 7.5 centimeter. How long can the 
#doorway be so that no more than 1 % of the people bump their heads?

```{r}
qnorm(0.01,175,7.5,lower.tail=F)
```

#A LIC salesman sells on the average 3 insurance policies per week. 
#Calculate the probability that in a given week he will sell
#A) Some policies
#B) 2 or more policies but less than 5 policies
#C) Assuming that there are 5 working days per week, what is the probability that in a given day he/she will sell one policy?

#A)
```{r}
1-dpois(0,3)
```
#B)
```{r}
sum(dpois(2:4,3))
```
#C
```{r}
dpois(1,3/5)
```


  



